---
title: "RMarkdown Group Activity"
author: "Write your Group Name"
date: "`r 2021-12-08`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal Group Activity

> To apply the princples of reproducible data science methods to a given dataset.

> To perform exploratory analysis including data importing, cleaning, wrangling and visualization using `tidy` methods.

> To document the analysis of the given dataset and prepare a report (in HTML and Word) using RMardown.

# About the Dataset

The dataset contains information on the deaths due to COVID-19 in 14 districts of Kerala state. This information is available for download from the Government of Kerala COVID-19 Dashboard (<https://dashboard.kerala.gov.in/covid/>).

### Variables of the dataset

| Variable Name | Description                           |
|---------------|---------------------------------------|
| sl_no         |  Serial Number                        |
| name          | Name of the Deceased                  |
| age           | Age of the Deceased                   |
| sex           | Gender of the Deceased                |
| district      | District of Residence of the Deceased |
| date_reported | Date of Reporting                     |
| date_of_death | Date of Death                         |


# Assignments

## 1. Load the required packges

```{r}
# library()
```

## 2, Import the Data

```{r}
# Hint: before you import the data, you check the extension of the file. 
# This may help you to chose between the read_csv(), read_excel, read_rds() functions

```


## 3, Check the class and structure of the dataset

```{r}
# Hint: Hint is in the question

```



## 4. Describing the dataset

Write an R code to look at the number of rows and columns.

```{r}
# Bonus points if you are using two different ways

```

Give quick summary of the dataset

```{r}
# Bonus points if you are using two different ways

```


What are the different types of variables in the dataset


```{r}

```

Provide your answer below:

<!-- Eg: there are 8 variables which are numeric, or double or charecter etc. -->


How many districts are there?

```{r}
# Bonus points if you are using two different ways 

```


How many deaths occured in each district?

```{r}
# Hint: you can use the count() function

```

According to this dataset, when did the maximum number of deaths occur?

```{r}

```


Which are the top five districts in COVID-19 deaths?

```{r}
# Hint: arrange?

```


Is there a delay between death and reporting of death?

If yes, how many days is the delay?

```{r}
# Hint: use mutate() to substract the relevant variables from each other, you can try the mean() function

```

Is this delay same across all the districts?

```{r}
# Hint: group_by()

```


Create a new categorical variable representing age as a dichotomous variable

```{r}
# Hint: ifelse(), case_when()

```


Create a new categorical variable representing the Wave of COVID

Hint: Use a cut off of 2021-04-01 

```{r}
# Hint: ifelse(), case_when()

```

-------
ASSIGNMENTS
-------

# Group A & B

#### What is the mean age of the deceased?
> Answer:



#### What is the difference in the mean age between both the genders?
> Answer:



#### Forumulate a hypothesis to check the association between age and gender?
> Answer:



#### Prepare an appropriate plot to visualise this relationships.
> Answer:



#### Which statistical tests should be applied here?
> Answer:



#### Please make a summary table using gtsummary for the same?
> Answer:



#### Interpret the findings
> Answer:




------

# Group C & D


#### What are distribution of deaths across time?
> Answer:




#### Visualize mortality of COVID-19 in Kerala in different districts
> Answer:



#### Which are the high burden district? Does these districts remain the same in both the COVID waves? Comment.
> Answer:



#### Is there an association between COVID-19 deaths and the waves of COVID?
> Answer:



#### Prepare an appropriate plot to visualise this relationships.
> Answer:



#### Which statistical tests should be applied here?
> Answer:



#### Please make a summary table using gtsummary for the same?
> Answer:



#### Interpret the findings
> Answer:





-------
# MEGA BONUS points if you use inline code to achieve this task!
-------