---
title: "RMarkdown Group Activity"
author: "Write your Group Name"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal Group Activity

> To apply the principles of reproducible data science methods to a given dataset.

> To perform exploratory analysis including data importing, cleaning, wrangling and visualization using `tidy` methods.

> To document the analysis of the given dataset and prepare a report (in HTML and Word) using RMardown.

# About the Dataset

The dataset contains information on the deaths due to COVID-19 in 14 districts of Kerala state. This information is available for download from the Government of Kerala COVID-19 Dashboard (<https://dashboard.kerala.gov.in/covid/>).

### Variables of the dataset

| Variable Name | Description                           |
|---------------|---------------------------------------|
| sl_no         | Serial Number                         |
| name          | Name of the Deceased                  |
| age           | Age of the Deceased                   |
| sex           | Gender of the Deceased                |
| district      | District of Residence of the Deceased |
| date_reported | Date of Reporting                     |
| date_of_death | Date of Death                         |

# Assignments

## 1. Load the required packges

```{r}
# library()
library(tidyverse)
library(gtsummary)
library(here)

```

## 2. Import the Data

```{r}
# Hint: before you import the data, you check the extension of the file. 
# This may help you to chose between the read_csv(), read_excel, read_rds() functions

# define file name
file_name <- "kerala_covid_deaths.rds"

# define file path
file_path <- here::here("data", file_name)
# remove file name, as it is no more necessary
rm(file_name)

# read data

df <- read_rds(file_path)
rm(file_path) # remove file path as it is no more necessary
```

## 3. Are the names of the dataset clean? If not, clean them.

```{r}
# Hint: Use the janitor package for this purpose
# Hint, Dont forget to save the data
names(df)

df <- df %>% 
  janitor::clean_names()

```

## 4. Check the class and structure of the dataset

```{r}
# Hint: Hint is in the question

df %>% 
  class()

df %>% 
  str()

```

## 5. Remove the variables not necessary for the analysis

```{r}
# Hint: select()
# variables "sl_no", "name", "place" and "history_traveler_contact" are not necessary

df %>% 
  dplyr::select(-c("sl_no", "name", "place", "history_traveler_contact"))  # negative sign means remove these
```

## 6. Describing the dataset

Write an R code to look at the number of rows and columns.

```{r}
# Bonus points if you are using two different ways

df %>% 
  dim()

df %>% 
  nrow()

df %>% 
  ncol()

```

Give quick summary of the dataset

```{r}
# Bonus points if you are using two different ways

df %>% 
  glimpse()


df %>% 
  skimr::skim()

```

What are the different types of variables in the dataset

```{r}
# What does the above output tell you?


```

Provide your answer below:

<!-- Eg: there are 8 variables which are numeric, or double or charecter etc. -->

> Answer: "character" "Date" "factor" "numeric"

How many districts are there?

```{r}
# Bonus points if you are using two different ways 
df %>% 
  distinct(district)

df %>% 
  pull(district) %>% 
  unique()

```

How many deaths occurred in each district?

```{r}
# Hint: you can use the count() function
df %>% 
  count(district)


```

According to this dataset, when did the maximum number of deaths occur?

```{r}
df %>% 
  count(date_reported) %>% 
  arrange(-n)  # order in the descending order
```

Which are the top five districts in COVID-19 deaths?

```{r}
# Hint: arrange?
df %>% 
  count(district) %>% 
  arrange(-n) %>% 
  slice(1:5) # select the top five
```

Is there a delay between death and reporting of death?

If yes, how many days is the delay?

```{r}
# Hint: use mutate() to substract the relevant variables from each other, you can try the mean() function
df %>% 
  mutate(
    delay = date_reported - date_of_death) %>%
  pull(delay) %>% 
  mean(na.rm = T) %>% 
  round(1)
```

Is this delay same across all the districts?

```{r}
# Hint: group_by()
df %>% 
  mutate(
    delay = date_reported - date_of_death) %>%
  group_by(district) %>%
  summarize(
    mean_delay = mean(delay, na.rm = T)) # remove missing values
```

Create a new categorical variable representing age as a dichotomous variable

```{r}
# Hint: ifelse(), case_when()
df <- df %>% 
  mutate(
    age_group = 
      ifelse(
        age <= 60, "<60 Years",">60 Years"))

df <- df %>% 
  mutate(
    age_group = case_when(
      age <= 60 ~ "<60 Years", 
      TRUE ~ ">60 Years"))

```

Create a new categorical variable representing the Wave of COVID

Hint: Use a cut off of 2021-04-01

```{r}
# Hint: ifelse(), case_when()
df <- df %>% 
  mutate(
    wave = ifelse(
      date_of_death <= "2021-04-01", "First Wave", "Second Wave"))  


df <- df %>% 
  mutate(
    wave = case_when(
      date_of_death <= "2021-04-01" ~ "First Wave",
      TRUE ~ "Second Wave"))
```

|             |
|-------------|
| ASSIGNMENTS |

# Group A & B

#### What is the mean age of the deceased?

> Answer:

#### What is the difference in the mean age between both the genders?

> Answer:

#### Forumulate a hypothesis to check the association between age and gender?

> Answer:

#### Prepare an appropriate plot to visualise this relationships.

> Answer:

#### Which statistical tests should be applied here?

> Answer:

#### Please make a summary table using gtsummary for the same?

> Answer:

#### Interpret the findings

> Answer:

------------------------------------------------------------------------

# Group C & D

#### What are distribution of deaths across time?

> Answer:

#### Visualize mortality of COVID-19 in Kerala in different districts

> Answer:

#### Which are the high burden district? Does these districts remain the same in both the COVID waves? Comment.

> Answer:

#### Is there an association between COVID-19 deaths and the waves of COVID?

> Answer:

#### Prepare an appropriate plot to visualise this relationships.

> Answer:

#### Which statistical tests should be applied here?

> Answer:

#### Please make a summary table using gtsummary for the same?

> Answer:

#### Interpret the findings

> Answer:

|                                                                   |
|-------------------------------------------------------------------|
| \# MEGA BONUS points if you use inline code to achieve this task! |
