---
title: "RMarkdown Group Activity"
author: "Group 3"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

# About the Dataset

The dataset contains information on the deaths due to COVID-19 in 14 districts of Kerala state. This information is available for download from the Government of Kerala COVID-19 Dashboard (<https://dashboard.kerala.gov.in/covid/>


## 1. Load packages

```{r}
# library()
library(tidyverse)
library(here)
library(gtsummary)
```

## 2. Import the Data

```{r warning=FALSE}

# define file path
df_path<- here::here("data","kerala_covid_deaths.rds")

# read data
df <- read_rds(here(df_path))
```


## 3. Are the names of the dataset clean? If not, clean them.

```{r}
df <- df %>% 
  janitor::clean_names()

names(df)
```

## 4. Check the class and structure of the dataset

```{r}

df %>% 
  class()

df %>% 
  str()

```


## 5. Remove the variables not necessary for the analysis

```{r}

df <- df %>% 
  select(-c("sl_no", "name", "place", "history_traveler_contact"))

view(df)
```
Here we have removedthe variables not necessary for the analysis.

## 6. Describing the dataset

Write an R code to look at the number of rows and columns.

```{r}

df %>% 
  dim()

df %>% 
  nrow()

df %>% 
  ncol()

df %>% 
  glimpse()

df %>% as_tibble()

```

Give quick summary of the dataset

```{r}

df %>% 
  glimpse()


df %>% 
  skimr::skim()

df %>% 
  tbl_summary()


```

What are the different types of variables in the dataset

```{r}
# What does the above output tell you?
class(df)

as_tibble(df)
```

How many districts are there?

```{r}

df %>% 
  distinct(district)

df %>% 
  count(district)


```

How many deaths occurred in each district?

```{r}

df %>% 
  count(district) %>% 
  arrange(n)


```

According to this dataset, when did the maximum number of deaths occur?

```{r}
 df %>% 
  count(date_reported) %>% 
  arrange(-n) 
```

#Maximum Number  of death occured on 2021-06-06.
#Which are the top five districts in COVID-19 deaths?

```{r}
df %>% 
  count(district) %>% 
  arrange(-n) %>% 
  slice(1:5)
```
TOP 5 Districts are: Trivandrum, Thrissur, kozhikode, Palakkad, Eranakulam 


#Is there a delay between death and reporting of death?
#If yes, how many days is the delay?

```{r}
# Hint: use mutate() to substract the relevant variables from each other, you can try the mean() function
df %>% 
  mutate(
    delay = date_reported - date_of_death) %>%
  pull(delay) %>% 
  mean(na.rm = T) %>% 
  round(1)
```
 
average Delay of 6.2 days is seen. 
 
#Is this delay same across all the districts?
```{r}

df %>% 
  mutate(
    delay = date_reported - date_of_death) %>%
  group_by(district) %>%
  summarize(
    mean_delay = mean(delay, na.rm = T))
```

No. There are variations across all the districts from mean.

#Create a new categorical variable representing age as a dichotomous variable

```{r}
df <- df %>% 
  mutate(
    age_group = 
      ifelse(
        age <= 60, "<60 Years",">60 Years"))

view(df)
```
Now, two categories have been created: <60 and >60.

#Create a new categorical variable representing the Wave of COVID
##Use a cut off of 2021-04-01

```{r}
df <- df %>% 
  mutate(
    wave = ifelse(
      date_of_death <= "2021-04-01", "First Wave", "Second Wave"))  


```

|             |
|-------------|
| ASSIGNMENTS |

------------------------------------------------------------------------

# Group C & D

#### What are distribution of deaths across time?

> Answer:

```{r}
df %>% 
  count(date_reported) %>% 
  arrange(-n) 


```


#### Visualize mortality of COVID-19 in Kerala in different districts

> Answer:

```{r}

df %>% 
  ggplot() +
  geom_bar(aes(x = district))
              
```


#### Which are the high burden district? Does these districts remain the same in both the COVID waves? Comment.

> Answer:trivandrum, thrissur

#### Is there an association between COVID-19 deaths and the waves of COVID?

> Answer:

```{r}

              
```

#### Prepare an appropriate plot to visualise this relationships.

> Answer:
```{r}

```
#### Which statistical tests should be applied here?

> Answer:

#### Please make a summary table using gtsummary for the same?

> Answer:

#### Interpret the findings

> Answer:

|                                                                   |
|-------------------------------------------------------------------|
| \# MEGA BONUS points if you use inline code to achieve this task! |
