---
title: "Inline R Code"
author: ""
date: "2021-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

```


```{r message=FALSE, warning=FALSE, include=FALSE}
## Load Packages
library(tidyverse)
library(gtsummary)
library(here)

```



```{r message=FALSE, warning=FALSE, include=FALSE}
# Import the Data

# define file name
file_name <- "kerala_covid_deaths.rds"

# define file path
file_path <- here::here("data", file_name)


# read data
df <- readRDS(file_path)

df <- df %>% janitor::clean_names() 
```




```{r include=FALSE}
df %>% pull(age) %>% mean(na.rm = T) %>% round(1)

sex_prop_table <- df %>% count(sex) %>% mutate(prop = round(((n / sum(n))*100),2))

```

The total number of participants in the study were `r df %>% nrow()`.  The number of males were `r sex_prop_table %>% filter(sex == "Male") %>% pull(n)`, (`r sex_prop_table %>% filter(sex == "Male") %>%  pull(prop)`%) and females were The number of males were `r sex_prop_table %>% filter(sex == "Female") %>% pull(n)`, (`r sex_prop_table %>% filter(sex == "Female") %>%  pull(prop)`%).

# Age

The mean age of the study population is `r df %>% pull(age) %>% mean(na.rm = T) %>% round(1)` $\pm$ `r df %>% pull(age) %>% sd(na.rm = T) %>% round(1)` years.


# Using GTSUMMARY package

```{r include=F}
library(gtsummary)
library(tidyverse)
t1 <-df %>% dplyr::select(sex) %>% tbl_summary()
```

The proportion of males in the study population is `r inline_text(t1, variable = sex, level = "Male", pattern = "{n} ({p}%)")` and for females is `r inline_text(t1, variable = sex, level = "Female", pattern = "{n} ({p}%)")`.


### Let us make a categorical variable for age group


```{r}
df <- df %>% 
  mutate(age_groups = ifelse(age >= 60, "> 60 years", "< 60 years")) %>% 
  mutate(age_groups = factor(age_groups, levels = c("> 60 years", "< 60 years"))) %>% 
  mutate(wave = ifelse(date_of_death >= "2021-04-01", "Second Wave", "First Wave")) %>% 
  mutate(wave = factor(wave))

```

```{r}
# Creating a logistic model

## with only age_groups as the explanatory variable
logistic_model1 <- glm(data = df, wave ~ age_groups , family = "binomial")

## with only sex as the explanatory variable
logistic_model2 <- glm(data = df, wave ~ sex, family = "binomial")

## with both age_groups and sex as the explanatory variable
logistic_model3 <- glm(data = df, wave ~ age_groups + sex, family = "binomial")
```


## with only age_groups as the explanatory variable
```{r}
tbl_regression(logistic_model1, exponentiate = T)
```


## with only sex as the explanatory variable
```{r}
tbl_regression(logistic_model2, exponentiate = T)
```


## with both age_groups and sex as the explanatory variable
```{r}
tbl_regression(logistic_model3, exponentiate = T)
```

# Let us now try to look at the districts and how they might explain the deaths
```{r}
# let us first decide on our reference district. For now let us assume Ernakulam as our reference district

# let build our model

logistic_model4 <- glm(data = df, wave ~ age_groups + sex + district, family = "binomial")
```

```{r}
tbl_regression(logistic_model4, exponentiate = T)
```








